---
title: "Statistical-Inference-Course-Project Part 2"
author: "Yigang"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---
# Part 2 Basic Inferential Data Analysis 

### Load data and get an overview of the date set

```{r}
#?ToothGrowth
#The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC).

data("ToothGrowth")
head(ToothGrowth)
summary(ToothGrowth)
```

### Visualizate the data set for anaylysis 

```{r}
# make dose as a factor has three levels
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
        
```

```{r}
#plot teeth length ~ dose level by supplement type
library("ggplot2")
ggplot(ToothGrowth, aes(x=dose, y=len, fill=supp))+
        geom_boxplot()+
        facet_grid(.~supp)
```

```{r}
#plot teeth length ~ supplement type by dose level
ggplot(ToothGrowth, aes(x=supp, y=len, fill=supp))+
        geom_boxplot()+
        facet_grid(.~dose)
```

- Discuss: Dose level and teeth length have a positive relationship for either supplement

### Hypothesis Tests

Use hypothesis tests to compare tooth growth by supp and dose

- Null Hypothesis: Dose type or delivery methods of Vitamin C has no effect on tooth growth
- significance level alpha = 0.05

```{r}
t.test(len ~ supp, data = ToothGrowth)
```

- Discuss: The overall result shows that p-value = 0.06063 is greater then 0.05 significance level, hence we do not reject the null hypothesis.

```{r}
#T test at dose level 0.5
dose1 <- subset(ToothGrowth, dose %in% c(0.5) ) 
t.test(len ~ supp, data = dose1)
```

- Discuss: The p-value = 0.006359 at dose level 0.5 is smaller then 0.05 significance level, hence we can reject the null hypothesis.

```{r}
#T test at dose level 0.1
dose1 <- subset(ToothGrowth, dose %in% c(1.0) ) 
t.test(len ~ supp, data = dose1)
```

- Discuss: The p-value = 0.001038 at dose level 1.0 is smaller then 0.05 significance 
level, hence we can reject the null hypothesis.

```{r}
#T test at dose level 2
dose1 <- subset(ToothGrowth, dose %in% c(2.0) ) 
t.test(len ~ supp, data = dose1)
```

- Discuss: The p-value = 0.9639 at dose level 2.0 is greater then 0.05 significance 
level, hence we can not reject the null hypothesis.

### Conclusions

- Dose level and teeth length have a positive relationship for either supplement
- Dose type or delivery methods of Vitamin C has no effect on tooth growth on dose level at 2.0
- Dose type or delivery methods of Vitamin C do have effect on tooth growth on dose level at 0.5 and 1.0



























